\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

\pagestyle{fancy}
\fancyhf{} % Clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
    \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
    \item\small{
        {#1 \vspace{-2pt}}
    }
}

\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & #2 \\
        \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
    \vspace{-1pt}\item
        \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
            \textbf{#1} & #2 \\
            \textit{\small#3} & \textit{\small #4} \\
        \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
        \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeEntry}[3][]{
    \item % This satisfies the outer itemize list
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
        % Left side content (Name | Company)
        \textbf{#2} \ifx\relax#1\relax \else \textbar\ \textit{\small #1} \fi
        % Right side content (Date)
        & \textit{\small #3}
    \end{tabular*}\vspace{-5pt}
    \resumeItemListStart
}

% And a command to close the entry cleanly
\newcommand{\resumeEntryEnd}{
    \resumeItemListEnd
}

\newcommand{\projectLink}[2]{\href{#1}{\underline{#2}}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING-----------------
\begin{center}
    \textbf{\Large James Onyegbosi} \\[1.5pt]
    \small
    \href{www.linkedin.com/in/james-onyegbosi-b04365270}{\underline{LinkedIn}} \textbar \hspace{1pt}
    \href{https://github.com/j4m3su0}{\underline{GitHub}} \textbar \hspace{1pt}
    \href{tel:+447943383063}{\underline{+44-7943-383063}} \textbar \hspace{1pt}
    \href{mailto:jamesuo.9116@gmail.com}{\underline{jamesuo.9116@gmail.com}}
\end{center}


%-----------EDUCATION-----------------
\section{Education}
    \resumeSubHeadingListStart
        \resumeSubheading
            {University of Birmingham}{Birmingham, United Kingdom}
            {Bachelor of Science in Mathematics and Computer Science}{Sep. 2025 -- Jul. 2028}
            \resumeItemListStart
                \resumeItem{Modules: Real Analysis, Linear Algebra, Probability \& Statistics, Data Structures \& Algorithms.}
                \resumeItem{Extracurriculars: Investment \& Finance Society (Analyst), Economics Society (Analyst).}
            \resumeItemListEnd    
        \resumeSubheading
            {Westminster City School}{London, United Kingdom}
            {A-Level's: A*AAB, GCSE's: 9988887765}{Sep. 2018 -- Jun. 2025}
            \resumeItemListStart
                \resumeItem{A-Level's: Mathematics (A*), Physics (A), Computer Science (A), Further Mathematics (B).}
                \resumeItem{GCSE's: Mathematics (8), Physics (8), Chemistry (8), Biology (8), English Literature (7), English Language (5), Geography (7), Art (9), Spanish (6), Religious Studies (9).}
                \resumeItem{Extracurriculars: Robotics Club (Lead Programmer), Pathways to Engineering, Table Tennis Club.}
            \resumeItemListEnd
    \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
    \resumeSubHeadingListStart
        \resumeSubheading
            {BIFS Investment Fund}{Birmingham, United Kingdom}
            {Equity Research Analyst}{Oct. 2025 -- Present}
            \resumeItemListStart
                \resumeItem{Conducted equity research on 10+ small-to-mid-cap technology companies, preparing comprehensive stock pitches and applying DCF and Comparable Company Analysis to support investment recommendations.}
                \resumeItem{Completed a 2-week intensive investment boot-camp, gaining hands-on experience in valuation, macroeconomic analysis, and professional pitch cycles.}
            \resumeItemListEnd
        \resumeSubheading
            {BECS Talking Theory}{Birmingham, United Kingdom}
            {Market Research Analyst}{Oct. 2025 -- Present}
            \resumeItemListStart
                \resumeItem{Authored and published in-depth analytical articles every 5 weeks, focusing on key trends and developments within the FX and commodities markets.}
                \resumeItem{Reached 1,000+ weekly readers by integrating data analysis and financial modelling into research, delivering rigorous, evidence-based insights on market dynamics and forecasts.}
            \resumeItemListEnd
        \resumeSubheading
            {Imperial College London}{London, United Kingdom}
            {Physics Summer School Participant}{Jul. 2024}
            \resumeItemListStart
                \resumeItem{Developed and simulated mathematical models for single and coupled oscillatory systems in Python over a 5-day period, converting second-order ODEs into solvable first-order systems using NumPy, SciPy, and Matplotlib.}
                \resumeItem{Achieved a Top-5 ranking among all research teams for presenting simulation findings to a panel of academics, demonstrating excellence in computational modelling, data analysis, and scientific communication.}
            \resumeItemListEnd
        \resumeSubheading
            {Westminster City School}{London, United Kingdom}
            {GCSE Mathematics \& Physics Tutor}{Feb. 2024 -- Jul. 2024}
            \resumeItemListStart
                \resumeItem{Selected from over 140 students to provide group tutoring sessions to Year 11 students, preparing for GCSE Mathematics and Physics examinations.}
                \resumeItem{Guided students to achieve Grade 7 or higher in GCSE examinations through targeted support and mentorship.}
            \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------HONOURS & AWARDS-----------------
\section{Honours \& Awards}
    \resumeSubHeadingListStart
        \resumeEntry[Student Robotics]{\projectLink{https://github.com/j4m3su0/student-robotics}{Top-15, Student Robotics 2023}}{Issued Feb. 2024}
            \resumeItem{Led a 10-person team to a Top-15 finish (virtual competition), designing and implementing maintainable Python software for the robot.}
            \resumeItem{Managed and facilitated bi-weekly team meetings over 8 months, ensuring project progression and seamless technical collaboration.}
        \resumeEntryEnd
    \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS & INTERESTS-----------------
\section{Technical Skills \& Interests}
    \resumeSubHeadingListStart
        \item \textbf{Programming Languages:} Python (NumPy, SciPy Matplotlib), C++, Java, SQL.
        \vspace{-7.5pt}
        \item \textbf{Certifications:} J.P. Morgan Chase Quantitative Research Virtual Experience Program (Forage). \vspace{-7.5pt}
        \item \textbf{Interests:} Table Tennis, Piano. \vspace{-7.5pt}
        
    \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
